---
title: "Uređivanje podataka"
output: html_document
date: "2024-01-05"
---

```{r setup, include=FALSE}
library(tidyverse)
library(gridExtra)
library(GGally)
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data <- read_csv("../data/IMDB_movie_dataset.csv")
head(data)
```


## Promjena redoslijeda stupaca

Dosadašnji redoslijed stupaca:
```{r}
names(data)
```
Promijenjeni redoslijed podataka i objašnjenja značenja imena stupaca:

```{r}
new_order <- c('movie_title', 'duration', 'director_name', 'director_facebook_likes', 'actor_1_name', 'actor_1_facebook_likes', 'actor_2_name', 'actor_2_facebook_likes', 'actor_3_name', 'actor_3_facebook_likes', 'num_user_for_reviews', 'num_critic_for_reviews', 'num_voted_users', 'cast_total_facebook_likes', 'movie_facebook_likes', 'plot_keywords', 'facenumber_in_poster', 'color', 'genres', 'title_year', 'language', 'country', 'content_rating', 'aspect_ratio', 'movie_imdb_link', 'gross', 'budget', 'imdb_score')
data <- data[, new_order]
```

Variable Name  | 	Description
-------|----------------------
`movie_title` | 	Title of the Movie
`duration` | 	Duration in minutes
`director_name`  | Name of the Director of the Movie
`director_facebook_likes` |  Number of likes of the Director on his Facebook Page
`actor_1_name`	 | Primary actor starring in the movie
`actor_1_facebook_likes`	 | Number of likes of the Actor_1 on his/her Facebook Page
`actor_2_name`	 | Other actor starring in the movie
`actor_2_facebook_likes` | 	Number of likes of the Actor_2 on his/her Facebook Page
`actor_3_name` | Other actor starring in the movie
`actor_3_facebook_likes`	 | Number of likes of the Actor_3 on his/her Facebook Page
`num_user_for_reviews`	 | Number of users who gave a review
`num_critic_for_reviews`	 | Number of critical reviews on imdb
`num_voted_users`	 | Number of people who voted for the movie
`cast_total_facebook_likes`	 | Total number of facebook likes of the entire cast of the movie
`movie_facebook_likes` | Number of Facebook likes in the movie page
`plot_keywords`	 | Keywords describing the movie plot
`facenumber_in_poster`	 | Number of the actor who featured in the movie poster
`color`	 | Film colorization. ‘Black and White’ or ‘Color’
`genres`	 | Film categorization like ‘Animation’, ‘Comedy’, ‘Romance’, ‘Horror’, ‘Sci-Fi’, ‘Action’, ‘Family’
`title_year	`	 | The year in which the movie is released (1916:2016)
`language`	 | English, Arabic, Chinese, French, German, Danish, Italian, Japanese etc.
`country`	 | Country where the movie is produced
`content_rating` | Content rating of the movie
`aspect_ratio`	 | Aspect ratio the movie was made in
`movie_imdb_link`	 | IMDB link of the movie
`gross`	 | Gross earnings of the movie in Dollars
`budget`	 | Budget of the movie in Dollars
`imdb_score`	 | IMDB Score of the movie on IMDB

**Faktorizacija stupca `color`:**

```{r}
data$color <- factor(data$color, levels = c("Color", "Black and White"))
```

Micanje duplikata:

```{r}
sum(duplicated(data))
```
```{r}
data <- distinct(data)
```


Eksportiranje podataka:

```{r}
write.csv(data, file = "../data/IMDB_movie_dataset_tidy.csv")
```

